---
title: "tidying"
author: "Paul Oldham"
date: "1 March 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidying UK company index

The UK company index raw file contains some noisy elements

Sectors to clarify. In some cases during the original research the team found it difficult to allocate a company to a sector. 

```{r}
clarify <- filter(ukindex, sector == "CLARIFY")
```

# Organisations lacking latitude and longitude

```{r}
ukindex1 <- drop_na(ukindex, latitude)
readr::write_csv(ukindex1, "ukindex/ukindex1.csv")
```


## Setting boundaries for the map

```{r}
library(geonames)
options(geonamesUsername = "yourusername")
uk_geonames_info <- GNcountryInfo(country = "UK")
uk_bounds <- uk_geonames_info %>% select(south, north, east, west)
readr::write_csv(uk_bounds, "ukindex/uk_bounds.csv")

save(uk_bounds, file = "ukindex/uk_bounds.rda")
```


## Add the UK Company Websites to the list as that makes a lot of sense. 

Needs an lapply approach I think because each website is different. It may actually need a forloop here rather than lapply

```{r}
lapply()


href <- "<a href="
    close_href <- ">"  #included for flexibility in labelling
    close_a <- "</a>"
 out <- paste0(href, shQuote(url), close_href, label, close_a)
```



## Adding Pop Ups

```{r}
map_url <- function(query, label = "NULL", type = "NULL") {
    href <- "<a href="
    close_href <- ">"  #included for flexibility in labelling
    close_a <- "</a>"
    if (type == "google") {
        query <- stringr::str_replace_all(query, " ", "+")
        google_base <- "https://www.google.co.uk/#q="
        url <- paste0(google_base, query)
        out <- paste0(href, shQuote(url), close_href, label, close_a)
    }
    if (type == "companies_house") {
        query <- stringr::str_replace_all(query, " ", "+")
        companies_base <- "https://beta.companieshouse.gov.uk/search?q="
        url <- paste0(companies_base, query)
        out <- paste0(href, shQuote(url), close_href, label, close_a)
    }
    if (type == "gbif") {
        query <- stringr::str_replace_all(query, " ", "+")
        gbif_base <- "http://www.gbif.org/species/search?q="
        url <- paste0(gbif_base, query)
        out <- paste0(href, shQuote(url), close_href, label, close_a)
    }
    if (type == "lens") {
        # note restriction to main jurisdictions and no stemming to reduce
        # duplication and false positives
        query <- stringr::str_replace_all(query, " ", "+")
        lens_base <- "https://www.lens.org/lens/search?q=applicant"
        url <- paste0(lens_base, "%3A", "%22", query, "%22", "&predicate=%26%26&l=en&f=true")
        out <- paste0(href, shQuote(url), close_href, label, close_a)
    }
    if (type == "espacenet"){
      query <- stringr::str_replace_all(query, " ", "+")
      espacenet_base <- "https://worldwide.espacenet.com/searchResults?submitted=true&locale=en_EP&DB=EPODOC&ST=advanced&TI=&AB=&PN=&AP=&PR=&PD=&PA="
      url <- paste0(espacenet_base, query)
      out <- paste0(href, shQuote(url), close_href, label, close_a)
      
    }
    out
}
```

```{r}
ukindex1$google <- map_url(ukindex1$company_name, label = "Lookup Google", type = "google")
ukindex1$companies_house <- map_url(ukindex1$company_name, label = "Lookup Companies House", 
    type = "companies_house")
ukindex1$espacenet <- map_url(ukindex1$company_name, label = "Lookup Patents", type = "espacenet")
```

combine the labels
```{r}
ukindex1$combined_label <- paste0("<br>", "<strong>", ukindex1$company_name, "</strong>", "</br>",  "<br>", ukindex1$google, "</br>", "<br>", ukindex1$companies_house, "</br>", "<br>", ukindex1$espacenet, "</br>")
```


test in leaflet

```{r}
    leaflet(ukindex1) %>% 
      addTiles() %>% fitBounds(lng1 = uk_bounds$west, lat1 = uk_bounds$north, lng2 = uk_bounds$east, lat2 = uk_bounds$south) %>% addCircleMarkers(lng = ukindex1$longitude, lat = ukindex1$latitude, popup = ukindex1$combined_label, radius = 1, weight = 2, opacity = 0.5, fill= TRUE, fillOpacity = 0.2)
```


Send to the app

```{r}

```

